---
title: "Multiple Linear Regression and Special Issues Assignment"
author: "Kathleen Coble"
date: "2/2/2020"
output:
  word_document: default
  html_document: default
---
```{r}
library(tidyverse)
library(GGally)
library(MASS)
```

```{r}
bike = read_csv("hour.csv")
```

```{r}
bike = bike %>% mutate(season = as_factor(as.character(season))) %>%
mutate(season = fct_recode(season,
"Spring" = "1",
"Summer" = "2",
"Fall" = "3",
"Winter" = "4"))
```

```{r}
bike = bike %>% mutate(yr = as_factor(as.character(yr)))
bike = bike %>% mutate(mnth = as_factor(as.character(mnth)))
bike = bike %>% mutate(hr = as_factor(as.character(hr)))
```

```{r}
bike = bike %>% mutate(holiday = as_factor(as.character(holiday))) %>%
mutate(holiday = fct_recode(holiday,
"NotHoliday" = "0",
"HoliDay" = "1"))
```

```{r}
bike = bike %>% mutate(workingday = as_factor(as.character(workingday))) %>%
mutate(workingday = fct_recode(workingday,
"NotWorkingDay" = "0",
"WorkingDay" = "1"))
```

```{r}
bike = bike %>% mutate(weathersit = as_factor(as.character(weathersit))) %>%
mutate(weathersit = fct_recode(weathersit,
"NoPrecip" = "1",
"Misty" = "2",
"LightPrecip" = "3",
"HeavyPrecip" = "4"))
```

```{r}
bike = bike %>% mutate(weekday = as_factor(as.character(weekday))) %>%
mutate(weekday = fct_recode(weekday,
"Monday" = "1",
"Tuesday" = "2",
"Wednesday" = "3",
"Thursday" = "4",
"Friday" = "5",
"Saturday" = "6",
"Sunday" = "0"))
```

#By converting yr, mnth, and hr into factors instead of numbers, we can look at them as objects. An example would be that the first few months of being in business had year represented as zero, which numberically might not be calculated properly if you wanted to know how many days it rained in the first few months of business.

```{r}
library(ggcorrplot)
ggpairs(bike, columns = c(3,7,9,10,17))
```
#The variables most correlated with "Count" are "Season", "Holiday", "WorkingDay", and "WeatherSit".

```{r}
allmod = bike %>% dplyr::select ("temp", "atemp", "hum", "windspeed", "count")

allmod = lm(temp~., bike)
summary(allmod)
```

```{r}
emptymod = lm(temp~1, bike)
summary(emptymod)
```

```{r}
forwardmod = stepAIC(emptymod, direction = "forward", scope = list(upper = allmod, lower = emptymod), trace = TRUE)
summary(forwardmod)
```

#Task 4: The variables included in my forward model are "temp", "atemp", "hum", "windspeed", and "count. The modelis good and seems to match our intuition/common sense.


```{r}
backmod = stepAIC(allmod, direction = "backward", trace = TRUE)
summary(backmod)
```

#Task 5: The forward and backward model are the same

#Task 6: WorkingDay is kicked out because it directly relates to the Weekday and the Holiday columns.

#Task 7: My concerns with the use of this model are that several variables appear to be predictors of other variables while they are not. An example is the workday, holiday, weekday variables as described above. 

