---
title: "Correlation and Simple Linear Regression Assignment"
author: "Kathleen Coble"
date: "2/2/2020"
output:
  word_document: default
  html_document: default
---

```{r}
library(tidyverse)
```

```{r}
library(ggplot2)
```

```{r}
library(GGally)
```

```{r}
library(ggplot2)
```

```{r}
air = airquality
```

#Task 1: There are 6 variables and 153 observations. There is some missing data. Temperature is most likely to be the Y variable.

```{r}
air2 = air %>% drop_na()
str(air2)
  
```

#Task 2: There are now 111 observations after removing the missing data.

```{r}
library(ggcorrplot)
```


```{r}
ggpairs(air2)
```

#Task 3: The variable "Temperature" is most strongly correlated with the “Ozone” variable, while "Wind" is least strongly correlated with the “Ozone” variable?

```{r}
ggplot(air2, aes(x=Temp, y=Ozone))+
  geom_point()
```

#Task4: Temperature and Ozone appear to have a high correlation.

```{r}
model1 = lm(Temp ~ Ozone, air2)
summary(model1)
```

```{r}
confint(model1)
```


#Task 5: 
# a. This is a good model because the p-value is less than .05, and the R squared value is almost .5 suggesting significance.
# b. The slope coefficient likely falls between 67 and 71.

```{r}
ggplot(air2, aes(x=Temp, y=Ozone))+
  geom_point()+
  geom_smooth(method="lm",se = FALSE)
```

#Task7: Prediction for ozone when temp is 80
```{r}
69.37059 + 0.20006 * 80
```

```{r}
temp_var = predict(model1, interval = "prediction")
new_df = cbind(air2, temp_var)
ggplot(new_df, aes(x=Temp, y=Ozone))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE, color = "red")+
  geom_line(aes(y=lwr), color = "red", linetype = "dashed")+
  geom_line(aes(x=upr), color = "red", linetype = "dashed")+
  theme_bw()
```

#Task 8: To ensure the linear regression model is valid, we look for:
# 1.	The predictor and response variable have a linear relationship - TRUE.
# 2.	Model errors (residuals) are independent - TRUE 
# 3.	Model residuals exhibit constant variance - TRUE
# 4.	Model residuals are Normally-distributed

#Task9: The model we constructed in Task 5 would be used to identify the lower and upper bounds. I have no concerns against recommending the model for use.






