---
output:
  word_document: default
  html_document: default
---
##Tidyverse Refresher

Libraries  
```{r}
library(tidyverse) #this is a comment
```

```{r}
cars = as.tibble(mtcars) #default dataset, no need to read-in dataset file
str(cars) #examine structure 
```

Select  
```{r}
cars %>% select(mpg) #does not create a new data frame
mpgonly = cars %>% select(mpg) #creates a new data frame called "mpgonly"
str(mpgonly) #examine the structure
glimpse(mpgonly) #alternative
```

Select multiple columns
```{r}
mpghp = cars %>% select(c(mpg,hp))
str(mpghp)
```

Filter  
```{r}
lowmpg = cars %>% filter(mpg < 20)
str(lowmpg)
```

Multiple condition filter  
```{r}
lowmpg8cyl = cars %>% filter(mpg < 20 & cyl == 8) #be sure to use == sign
str(lowmpg8cyl)
```

Mutate  
```{r}
cars = cars %>% mutate(hpratio = hp/mpg)
str(cars)
```

Grouping and Summarise  
```{r}
by_cyl = cars %>% group_by(cyl) %>% summarise(avghp = mean(hp))
by_cyl #display the newly grouped and summarized data
```

ggplot2  (Scatterplot)
```{r}
ggplot(cars, aes(x = hp, y = mpg)) + geom_point() + theme_bw()
```

Barplot (count)
```{r}
ggplot(cars, aes(x=cyl)) + geom_bar() + theme_bw()
```

Barplot (count with color by "am" variable (automatic vs. manual transmission))  
```{r}
ggplot(cars, aes(x=cyl, fill = as.factor(am))) + geom_bar() + theme_bw() #use as.factor to convert (only in the ggplot function, not in the data frame) "am" to a categorical variable to use for fill
```

Non-stacked version of same thing  
```{r}  
ggplot(cars, aes(x=cyl, fill = as.factor(am))) + geom_bar(position=position_dodge()) + theme_bw() #position=position_dodge() to unstack
```

Line plot (typically used to show how a quantity changes or evolves over time, this example is a bit forced, as a scatterplot would be more appropriate)  
```{r}
ggplot(cars, aes(x=hp, y=qsec)) + geom_line() + theme_bw() #without points
ggplot(cars, aes(x=hp, y=qsec)) + geom_line() + geom_point() + theme_bw() #with points
```




